Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-21 extended_catalog/paper/extended_catalog.tex
eps
more plots

\documentclass[12pt,preprint]{aastex}
%\documentclass[preprint]{aastex}

\bibliographystyle{apj}
\newcommand{\etal}{et al.}

\usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}

@@

\newcommand{\hl}[1]{{\color{red}#1}}

@@

For extended sources with an assumed radially symmetric shape,
we use a semi-analytic calculation to speed up the calculation of
the expected photon distribution. The expected photon 
distribution can be written as
\begin{equation}
  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r'^2 dr' d\phi'
\end{equation}
For the LAT, the PSF can be parameterized by a {\em King function}
\begin{equation}
  \text{PSF}(r) = 
  \frac{1}{2\pi\sigma^2}
  \left(1-\frac{1}{\gamma}\right)
  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
\end{equation}
where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
\citep{matthew_kerr_thesis}.  For radially symmetric extended sources,
the angular part of the integral can be evaluated analytically
\begin{align}
  \text{PDF}(u) & = \int_0^\infty r'^2 dr'
  I_\text{src}(v) 
  \int_0^{2\pi} d\phi' 
  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
  \\
  & = \int_0^\infty dv
  I_\text{src}(v) 
  \left(\frac{\gamma-1}{\gamma}\right)
  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
\end{align}
where $v=(r'/\sigma)^2/2$ and ${}_2F_1$ is the Gaussian hypergeometric
function.  This convolution formula reduces the expected photon
distribution to a single numerical integral.

@@

\hl{1
This extended source is spatially coincident with the middle-aged
SNR Puppis A.  Puppis A has been studied in detail in radio
(\cite{puppis_a_vla}, and references therein) and  X-ray 
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
The highest resolution image of the entire source was obtained
by \rosat and contours corresponding to this
image are overlaid on figure~\ref{1FGL_J0823.3-4248} and match the
inferred \gev size \citep{rosat_puppis_a}.
Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
which leads to a 1-100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.

No molecular clouds have been observed directly ajacent to Puppis A 
\citep{co_eastern_puppis_a}.
This is similar to the the LAT detected SNR the Cyngus Loop \citep{cygnus_loop_lat}.
The luminolsity of Puppis A is also smaller than that of 
other SNRs believed to interact with molecular clouds
\citep{w51c,ic443,w44,w28,w49b_lat}.
The \gev emission could therefore be explained by the interaction
of accelerated particles by interstellar matter or fields, similar
to the emission mechanism suggested for the Cygnus Loop SNR
\citep{cygnus_loop_lat}.
}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{ic443_plots/four_plots_ic443.eps}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
    \caption{
    Counts and test statistic profiles for the SNR IC443. (a) \ts
    vs. extension of the source. (b) \tsext for individual energy bands. (c)
    observed radial profile of counts in comparison to the expected profiles
    for a point source (blue) and a spatially extended source (red) . (d)
    smoothed count map after subtraction of the diffuse emission compared
    to the LAT PSF (inset).  Plots (a), (c), and (d) use only 1-100 \gev photons. 
    Plots (c) and (d)
    use only photons which converted in the front
    part of the detector and have an improved angular resolution.
    }
    \label{four_plots_ic443}
  \end{center}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/compare_disk_gauss.eps}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/plot.py
    \end{center}
    \caption{
    A comparison of a Gaussian and disk like surface brightness profile
    of extended sources before and after convolving with the PSF for two
    energy ranges.  The black line is the PSF that would be observed
    for a power-law source of spectral index 2. The dashed red line
    is the brightness profile of a Gaussian with $\rsixeight=0\fdg5$.
    The dashed blue line is the brightness profile for a uniform disk
    with $\rsixeight=0\fdg5$.  The solid red and blue lines show the
    convolution of the Gaussian and uniform disk brightness profiles
    with the LAT PSF.
    }\label{compare_disk_gauss}
  \end{figure}

@@

\colhead{Spectral Index}&
\colhead{Flux\tablenotemark{(a)}}&
\colhead{$N_\text{sims}$}&
\colhead{$\langle\ts\rangle$}\\
\colhead{}&
\colhead{\phflux}&
\colhead{}&
\colhead{}\\
}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/ts_ext_emin_1000.eps}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
    \end{center}
    \caption{
    Distribution of the test statistic \tsext of a likelihood ratio
    test when fitting the extension of a point source.  The four plots
    represent simulated point sources of different spectral indices and
    the different colors represent point sources with different 100 \mev
    to 100 \gev integral fluxes.  The dashed red line is the cumulative
    density function of equation~\ref{ts_ext_distribution}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.eps}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
    \end{center}
    \caption{
    The detection threshold ($\langle\tsext\rangle=16$) to resolve a
    uniform disk extended source for a two-year exposure.  All sources
    have an assumed power-law spectrum and the different colors correspond
    to different simulated spectral indices.  The solid line is the
    detection threshold using photons with energy between 100 \mev and 100
    \gev while the dashed line is the threshold using 1-100 \gev photons.
    }\label{index_sensitivity}
  \end{figure}

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/all_sensitivity.eps}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
    \end{center}
    \caption{the LAT detection threshold for four spectral indices and
    three background (1x, 10x, and 100x the Sreekumar-like isotropic
    spectrum) for a two-year exposure. The left plots are the detection
    threshold when using 1-100 \gev photons and the right plots are
    the detection threshold when using 10-100 \gev photons.  The flux
    is integrated only in the selected energy range.  Overlaid on this
    plot are the LAT detected extended sources placed by their nearby
    Galactic diffuse emission and color coded by their spectral index.
    The black point in plot (d) below the green line is MSH 15-52 which
    was found by our analysis to have $\tsext=6.5$.  
    }\label{all_sensitivity} 
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/time_sensitivity.eps}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
    \end{center}
    \caption{
    \hl{
    The LAT's projected detection threshold to extension after 10 years for a power-law
    source of spectral index 2 against 10 times the isotropic background
    in the energy range from 1-100 \gev (solid red) and 10-100 \gev
    (dashed blue). The solid gray region is the 
    detection threshold assuming the sensitivity improves from the 2
    year threshold by the square root of time (top edge) and linearly with
    time (bottom edge).  The lower plot shows the factor increase in
    sensitivity.  For small extended sources, our detection threshold
    improves by a factor better than the square root of time. 
    }
    }\label{time_sensitivity}
  \end{figure}

\begin{figure}
  \begin{center}
  \includegraphics{ic443_plots/res_tsmap_ic443.eps}
  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{source_plots/example_bad_fit.eps}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
    \caption{
    A diffuse-emission-subtracted 1-100 \gev counts map of the region
    around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 Gaussian kernel. The
    red cross and circle are the center and size of the best fit radially
    symmetric source with a uniform intensity profile. The result is
    statistically significant, but the extension encompasses many catalog
    sources and the emission does not look to be uniform. Instead,
    this source is probably fitting large-scale diffuse residual
    features. Although the fit is statistically significant, it likely
    corresponds to residual features of inaccurately modeled diffuse
    emission picked up by the fit.  We manually discard candidates that
    appear like this.
    }
    \label{example_bad_fit}
  \end{center}
\end{figure}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{source_plots/agn.eps}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v2/agn.py
    \end{center}
    \caption{The cumulative density of \tsext for 783 of the clean
    AGN in 2LAC which are significant above 1 \gev.  AGNs are too far
    and too small to be resolved by the LAT. Therefore, the cumulative
    density of $\tsext$ is expected to follow a $\chi^2/2$ distribution
    (equation~\ref{ts_ext_distribution}).     
    }\label{agn_ts_ext}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J0823.3-4248}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v7/source_1FGL_J0823.3-4248.pdf
  \caption{A diffuse-emission-subtracted 1-100
  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
  by a 0\fdg1 Gaussian kernel.  The red star is the 2FGL position
  of this source.  The red cross and circle are the best fit position
  and extension of this source assuming a radially symmetric uniform
  surface brightness.  The two green stars are the positions of the
  sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which were removed
  because they are part of the extended source.  The lower right inset
  is the model predicted emission from a point source with the same
  spectrum as 2FGL\,J0823.4-4305 smoothed by the same Gaussian kernel.
  This source is spatially coincident with the Puppis A SNR. The
  light blue contours correspond to the X-ray image of Puppis A observed by 
  \rosat
  \citep{rosat_puppis_a}. 
  }\label{1FGL_J0823.3-4248}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1628.6-2419c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v7/run.py
  \caption{
    \hl{
  A diffuse-emission-subtracted 1-100 \gev counts map of (a) the region
  around 2FGL\,J1627.0-2425 smoothed by a 0\fdg1 Gaussian kernel (b)
  also the emission from the background source 2FGL\,J1625.7-2526
  subtracted.  The red star is the 2FGL position of this source.
  The red cross and circle are the best position and extension of this
  source assuming a radially symmetric uniform surface brightness. The
  contours in (a) correspond to the 100 micrometer image observed by
  IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
  ${}^{12}\text{CO}$ ($J=1\rightarrow 0$) emission integrated from -8 \km/\s
  to 20 \km/\s.  They are from \cite{co_rho_ophiuci}, were cleaned using
  the moment-masking technique \citep{masking_moment_2011}, and have
  been smoothed by a 0\fdg25 Gaussian kernel.
    }
  }\label{1FGL_J1628.6-2419c}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_RX_J1713.7-3946}
    % this plot came from
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
  \end{center}
  \caption{A diffuse-emission-subtracted 1-100 \gev
  counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
  a 0\fdg25 Gaussian kernel and (b) also the emission 
  from the background sources subtracted.
  This source is spatially
  coincident with RX J1713.7-3946 was was recently reported by
  \citep{rx_j1713_lat}.  The light blue contours correspond to the \tev image
  observed by H.E.S.S. \citep{rx_j1713_hess}.  The region was analyzed
  with the same background model as \citep{rx_j1713_lat}.  Source A (blue
  cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
  The gray crosses represent from left to right the position of source B
  and C which were added to the background model. 
  }\label{2FGL_J1712.4-3941}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_Vela_Jr}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v7/run.py
  \caption{A diffuse-emission-subtracted 10-100
  \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
  by a 0\fdg25 Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
  and circle are the best fit position and extension of the source
  assuming a radially
  symmetric uniform surface brightness.  The inner three green stars
  are (from left to right) 2FGL\,J0853.5-4711, 2FGL\,J0855.4-4625,
  and 2FGL\,J0848.5-4535 which were removed because they are part of
  the extended source.  The farther away green stars are (from left to
  right) 2FGL\,J0901.7-4655 and 2FGL\,J0858.0-4815 which were removed
  because they were not significant above 10 \gev.  The blue cross
  is the relocalized position of 2FGL\,J0854.7-4501.  This extended
  source is spatially coincident with the Vela Jr SNR.  The light
  blue contours correspond to the \tev image of Vela Jr. observed by H.E.S.S
  \citep{vela_jr_hess}.
  }\label{Vela_Jr}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=eps,ext=.eps,read=.eps]{source_plots/source_1FGL_J1613.6-5100c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v7/run.py
  \caption{
    A diffuse-emission-subtracted 10-100
    \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0\fdg1
    Gaussian kernel.  The red stars are the catalog positions of these
    sources.  The red stars and circles are the best fit positions and
    extensions of these sources 
    assuming a radially
    symmetric uniform surface brightness.
    The green star inside the extension of 2FGL\,J1615.2-5138  is
    2FGL\,J1614.9-5212 which was removed because it is part of the
    extended source.  The green stars to the left are 2FGL\,J1619.7-5040c
    and 2FGL\,J1620.6-5111c which were removed because they were
    not significant above 10\gev. These are shown as green stars.
    The light blue
    contours correspond to the \tev image 
    of the extended sources
    HESS\,J1616-508 (left) and the extended source HESS\,J1614-518
    (right)
    observed by H.E.S.S
    \citep{hess_plane_survey}
    2FGL\,J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
    2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
  }\label{1FGL_J1613.6-5100c}
\end{figure}

>>>>

\documentclass[12pt,preprint]{aastex}

\bibliographystyle{apj}

\newif\ifcolorfigure
%\colorfiguretrue
\colorfigurefalse

@@

\usepackage{color}
\newcommand{\hl}[1]{{\color{red}#1}}

@@

For extended sources with an assumed radially symmetric shape,
we use a semi-analytic calculation to speed up the calculation of
the expected photon distribution. The expected photon 
distribution can be written as
\begin{equation}
  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r' dr' d\phi'
\end{equation}
For the LAT, the PSF can be parameterized by a {\em King function}
\begin{equation}
  \text{PSF}(r) = 
  \frac{1}{2\pi\sigma^2}
  \left(1-\frac{1}{\gamma}\right)
  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
\end{equation}
where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
\citep{matthew_kerr_thesis}.  For radially symmetric extended sources,
the angular part of the integral can be evaluated analytically
\begin{align}
  \text{PDF}(u) & = \int_0^\infty r' dr'
  I_\text{src}(v) 
  \int_0^{2\pi} d\phi' 
  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
  \\
  & = \int_0^\infty dv
  I_\text{src}(v) 
  \left(\frac{\gamma-1}{\gamma}\right)
  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
\end{align}
where $v=(r'/\sigma)^2/2$ and ${}_2F_1$ is the Gaussian hypergeometric
function.  This convolution formula reduces the expected photon
distribution to a single numerical integral.

@@

\hl{1
This extended source is spatially coincident with the middle-aged
SNR Puppis A.  Puppis A has been studied in detail in radio
(\cite{puppis_a_vla}, and references therein) and  X-ray 
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
Mosaic \rosat observations of Puppis A produced the highest
resolution X-ray image of the source
and contours corresponding to this
image are overlaid on figure~\ref{1FGL_J0823.3-4248} and match the
inferred \gev size \citep{rosat_puppis_a}.
Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
which leads to a 1-100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.

No molecular clouds have been observed directly ajacent to Puppis A 
\citep{co_eastern_puppis_a}.
This is similar to the LAT detected SNR the Cyngus Loop \citep{cygnus_loop_lat}.
The luminolsity of Puppis A is also smaller than that of 
other SNRs believed to interact with molecular clouds
\citep{w51c,ic443,w44,w28,w49b_lat}.
The \gev emission could therefore be explained by the interaction
of accelerated particles by interstellar matter or fields, similar
to the emission mechanism suggested for the Cygnus Loop SNR
\citep{cygnus_loop_lat}.
}

@@

\clearpage
\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{ic443_plots/four_plots_ic443_color.eps}
    \else
      \includegraphics{ic443_plots/four_plots_ic443_bw.eps}
    \fi
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/four_plots_ic443/v1/run.py
    \caption{
    Counts and test statistic profiles for the SNR IC443. (a) \ts
    vs. extension of the source. (b) \tsext for individual energy
    bands. (c) observed radial profile of counts in comparison to the
    expected profiles for a spatially extended source (solid and colored
    red in the online version) and for a point source (dashed and colored
    blue in the online version).  (d) smoothed count map after subtraction
    of the diffuse emission compared to the LAT PSF (inset).  Plots (a),
    (c), and (d) use only 1-100 \gev photons.  Plots (c) and (d) use
    only photons which converted in the front part of the detector and
    have an improved angular resolution.
    }
    \label{four_plots_ic443}
  \end{center}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{mc_plots/compare_disk_gauss_color.eps}
    \else
      \includegraphics{mc_plots/compare_disk_gauss_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v3/plot.py
    \end{center}
    \caption{
    A comparison of a Gaussian and disk surface brightness profiles
    of extended sources before and after convolving with the PSF for two
    energy ranges.  The solid black line is the PSF that would be observed
    for a power-law source of spectral index 2. The dashed line
    and the dash-dot line are 
    the brightness profile of a Gaussian with $\rsixeight=0\fdg5$
    and the convolution of this profile with the LAT PSF respectivly
    (colored red in the online version)
    The dash-dot-dot and the dot-dot line are the brightness profile of a uniform disk
    with $\rsixeight=0\fdg5$ and the convolution 
    of this profile with the LAT PSF respectivly (colored blue in the online version).
    }\label{compare_disk_gauss}
  \end{figure}

@@

\colhead{Spectral Index}&
\colhead{Flux\tablenotemark{(a)}}&
\colhead{$N_\text{sims}$}&
\colhead{$\langle\ts\rangle$}\\
\colhead{}&
\colhead{(\phflux)}&
\colhead{}&
\colhead{}\\
}

@@

\clearpage
\begin{figure}
  \begin{center}
    \ifcolorfigure
    \includegraphics{mc_plots/ts_ext_emin_1000_color.eps}
    \else
    \includegraphics{mc_plots/ts_ext_emin_1000_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v4/plot.py
    \end{center}
    \caption{
    Distribution of the test statistic \tsext of a likelihood ratio
    test when fitting the extension of a point source.  The four plots
    represent simulated point sources of different spectral indices and
    the different lines (colored in the online version) 
    represent point sources with different 100 \mev
    to 100 \gev integral fluxes.  The dashed line (colored red in online version)
    is the cumulative
    density function of equation~\ref{ts_ext_distribution}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \ifcolorfigure
    \includegraphics{mc_plots/index_sensitivity_color.eps}
    \else
    \includegraphics{mc_plots/index_sensitivity_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
    \end{center}
    \caption{
    The detection threshold ($\langle\tsext\rangle=16$) to resolve a
    uniform disk extended source for a two-year exposure.  All sources
    have an assumed power-law spectrum and the different colors correspond
    to different simulated spectral indices.  The solid line is the
    detection threshold using photons with energy between 100 \mev and 100
    \gev while the dashed line is the threshold using 1-100 \gev photons.
    }\label{index_sensitivity}
  \end{figure}

\clearpage
\begin{figure}
  \begin{center}
    \ifcolorfigure
    \includegraphics{mc_plots/all_sensitivity_color.eps}
    \else
    \includegraphics{mc_plots/all_sensitivity_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
    \end{center}
    \caption{the LAT detection threshold for four spectral indices and
    three background (1x, 10x, and 100x the Sreekumar-like isotropic
    spectrum) for a two-year exposure. The left plots are the detection
    threshold when using 1-100 \gev photons and the right plots are
    the detection threshold when using 10-100 \gev photons.  The flux
    is integrated only in the selected energy range.  Overlaid on this
    plot are the LAT detected extended sources placed by the magnitude of
    the nearby Galactic diffuse emission and the energy range they were
    analyzed with.  The stars (colored red in the electronic version) are
    sources with a spectral index closer to 1.5, the triangles (colored
    blue) an index closer to 2, and the circles (colored green) an index
    closer to 2.5 The circle in plot (d) below the sensitivity line is
    MSH 15-52 which was found by our analysis to have $\tsext=6.5$.
    }\label{all_sensitivity} 
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{mc_plots/time_sensitivity_color.eps}
    \else
      \includegraphics{mc_plots/time_sensitivity_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
    \end{center}
    \caption{
    \hl{
    The LAT's projected detection threshold to extension after 10 years for a power-law
    source of spectral index 2 against 10 times the isotropic background
    in the energy range from 1 \gev to 100 \gev (solid line colored red in the electronic
    version) and 10 \gev to 100 \gev
    (dashed line colored blue in the electronic version). The solid gray region is the 
    detection threshold assuming the sensitivity improves from 2 to 10
    years by the square root of time (top edge) and linearly with
    time (bottom edge).  The lower plot shows the factor increase in
    sensitivity.  For small extended sources, our detection threshold
    to the extension of a source will improve by a factor better than the square root of time. 
    }
    }\label{time_sensitivity}
  \end{figure}

\begin{figure}
  \begin{center}
  \ifcolorfigure
    \includegraphics{ic443_plots/res_tsmap_ic443_color.eps}
    \else
    \includegraphics{ic443_plots/res_tsmap_ic443_bw.eps}
    \fi
  % plot from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/res_tsmap_ic443/v1

@@

\clearpage
\begin{figure}
  \begin{center}
    \ifcolorfigure
    \includegraphics{source_plots/example_bad_fit_color.eps}
    \else
    \includegraphics{source_plots/example_bad_fit_bw.eps}
    \fi
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
    \caption{
    A diffuse-emission-subtracted 1-100 \gev counts map of the region
    around 2FGL\,J1856.2+0450c smoothed by a 0\fdg1 Gaussian kernel. The
    plus and circle (colored red in the online version) represent the
    center and size of the best fit radially symmetric source with
    a uniform intensity profile.  The black crosses represent the
    position of background 2FGL sources.  The result is statistically
    significant, but the extension encompasses many catalog sources and
    the emission does not look to be uniform. Instead, this source is
    probably fitting large-scale diffuse residual features. Although
    the fit is statistically significant, it likely corresponds to
    residual features of inaccurately modeled diffuse emission picked
    up by the fit.  We manually discard candidates that appear like this.
    }
    \label{example_bad_fit}
  \end{center}
\end{figure}

@@

\clearpage
\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{source_plots/agn_color.eps}
    \else
      \includegraphics{source_plots/agn_bw.eps}
    \fi
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/agn/v6/agn.py
    \end{center}
    \caption{The cumulative density of \tsext for 783 of the clean
    AGN in 2LAC which are significant above 1 \gev calculted with \pointlike (the dashed line
    colored blue in the electronic version)
    and with \gtlike (the solid line colored red in the electronic version).  AGNs are too far
    and too small to be resolved by the LAT. Therefore, the cumulative
    density of $\tsext$ is expected to follow a $\chi^2/2$ distribution
    (equation~\ref{ts_ext_distribution}) and is the dash-dotted line (colored
    red in the electronic version).
    }\label{agn_ts_ext}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{source_plots/source_Puppis_A_color.eps}
    \else
      \includegraphics{source_plots/source_Puppis_A_bw.eps}
    \fi
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v7/run.py
  \caption{A diffuse-emission-subtracted 1 \gev to 100
  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
  by a 0\fdg1 Gaussian kernel.  
  The triangle (colored red in the online version)
  is the 2FGL position
  of this source.  The cross and circle (colored red) are the best fit position
  and extension of this source assuming a radially symmetric uniform
  surface brightness.  The two stars (colored green) are the positions of the
  sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which were removed
  because they are part of the extended source.  The lower right inset
  is the model predicted emission from a point source with the same
  spectrum as 2FGL\,J0823.4-4305 smoothed by the same Gaussian kernel.
  This source is spatially coincident with the Puppis A SNR. The
  light blue contours correspond to the X-ray image of Puppis A observed by 
  \rosat
  \citep{rosat_puppis_a}. 
  }\label{1FGL_J0823.3-4248}
\end{figure}

\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{source_plots/source_Ophiuchus_color.eps}
    \else
      \includegraphics{source_plots/source_Ophiuchus_bw.eps}
    \fi
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v7/run.py
  \caption{
    \hl{
  A diffuse-emission-subtracted 1-100 \gev counts map of (a) the region
  around 2FGL\,J1627.0-2425 smoothed by a 0\fdg1 Gaussian kernel (b)
  also the emission from the background source 2FGL\,J1625.7-2526
  subtracted.  The red star is the 2FGL position of this source.
  The red cross and circle are the best position and extension of this
  source assuming a radially symmetric uniform surface brightness. The
  contours in (a) correspond to the 100 micrometer image observed by
  IRAS \citep{iras_rho_ophiuci}.  The contours in (b) correspond to
  ${}^{12}\text{CO}$ ($J=1\rightarrow 0$) emission integrated from -8 \km/\s
  to 20 \km/\s.  They are from \cite{co_rho_ophiuci}, were cleaned using
  the moment-masking technique \citep{masking_moment_2011}, and have
  been smoothed by a 0\fdg25 Gaussian kernel.
    }
  }\label{1FGL_J1628.6-2419c}
\end{figure}

\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{source_plots/source_RX_J1713.7-3946_color.eps}
    \else
      \includegraphics{source_plots/source_RX_J1713.7-3946_bw.eps}
    \fi
    % this plot came from
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
  \end{center}
  \caption{A diffuse-emission-subtracted 1-100 \gev
  counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
  a 0\fdg25 Gaussian kernel and (b) also the emission 
  from the background sources subtracted.
  This source is spatially
  coincident with RX J1713.7-3946 was was recently reported by
  \citep{rx_j1713_lat}.  The light blue contours correspond to the \tev image
  observed by H.E.S.S. \citep{rx_j1713_hess}.  The region was analyzed
  with the same background model as \citep{rx_j1713_lat}.  Source A (blue
  cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
  The gray crosses represent from left to right the position of source B
  and C which were added to the background model. 
  }\label{2FGL_J1712.4-3941}
\end{figure}

\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{source_plots/source_Vela_Jr_color.eps}
    \else
      \includegraphics{source_plots/source_Vela_Jr_bw.eps}
    \fi
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v7/run.py
  \caption{A diffuse-emission-subtracted 10-100
  \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
  by a 0\fdg25 Gaussian kernel. The red star is the 2FGL position of this source.  The red cross
  and circle are the best fit position and extension of the source
  assuming a radially
  symmetric uniform surface brightness.  The inner three green stars
  are (from left to right) 2FGL\,J0853.5-4711, 2FGL\,J0855.4-4625,
  and 2FGL\,J0848.5-4535 which were removed because they are part of
  the extended source.  The farther away green stars are (from left to
  right) 2FGL\,J0901.7-4655 and 2FGL\,J0858.0-4815 which were removed
  because they were not significant above 10 \gev.  The blue cross
  is the relocalized position of 2FGL\,J0854.7-4501.  This extended
  source is spatially coincident with the Vela Jr SNR.  The light
  blue contours correspond to the \tev image of Vela Jr. observed by H.E.S.S
  \citep{vela_jr_hess}.
  }\label{Vela_Jr}
\end{figure}

\begin{figure}
  \begin{center}
    \ifcolorfigure
      \includegraphics{source_plots/source_HESS_J1614-518_color.eps}
    \else
      \includegraphics{source_plots/source_HESS_J1614-518_bw.eps}
    \fi
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v7/run.py
  \caption{
    A diffuse-emission-subtracted 10-100
    \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0\fdg1
    Gaussian kernel.  The red stars are the catalog positions of these
    sources.  The red stars and circles are the best fit positions and
    extensions of these sources 
    assuming a radially
    symmetric uniform surface brightness.
    The green star inside the extension of 2FGL\,J1615.2-5138  is
    2FGL\,J1614.9-5212 which was removed because it is part of the
    extended source.  The green stars to the left are 2FGL\,J1619.7-5040c
    and 2FGL\,J1620.6-5111c which were removed because they were
    not significant above 10\gev. These are shown as green stars.
    The light blue
    contours correspond to the \tev image 
    of the extended sources
    HESS\,J1616-508 (left) and the extended source HESS\,J1614-518
    (right)
    observed by H.E.S.S
    \citep{hess_plane_survey}
    2FGL\,J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
    2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
  }\label{1FGL_J1613.6-5100c}
\end{figure}
